Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-11-21 analysis/paper/sim_survey_paper.Rmd
Revisit methods. Start adding plots for test_surveys output. Also set-up a manual cache for the plots.

```{r setup, include=FALSE}
# devtools::install_github("rstudio/rmarkdown@v1.10")
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      dev = "png",
                      dpi = 300)
knitr::opts_knit$set(root.dir = "../..")
```

```{r packages, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
Sys.setenv("MAPBOX_TOKEN" = "pk.eyJ1IjoicGF1bHJlZ3VsYXIiLCJhIjoiY2pueGIxejMxMGM0MjNqbjR1aXdwYm92bSJ9.R-t1SCa0VHKf4N-PQmYI5Q")
source("analysis/paper/helper_functions.R")
```

@@

The construction of the SimSurvey package was motivated by a regional need for assessing the sampling design of trawl surveys conducted along the Newfoundland and Labrador shelf by Fisheries and Oceans Canada. As a tangible first step, we focused our efforts on emulating data from the survey of cod in NAFO division 3Ps since it is one of the most dynamic and heavily sampled stocks in the region. Below we outline the equations behind a series of SimSurvey functions that were used to simulate survey data with similar features to data obtained by the survey of 3Ps cod. The settings were iteratively modified until it was difficult to distinguish the simulated data from real survey data. Here we evaluate the efficacy of alternate sampling protocol by assessing deviation between stratified estimates of abundance [@Smith1981] from the true abundance available to the survey. While assessing model-based analyses was an option, we focused on the design-based stratified analysis for simplicity and because of its widespread use. See Table \@ref(tab:par) for a description of the code used to generate the case study results.

Table: (\#tab:par) - Main function calls, with argument descriptions and associated parameter symbols, used to simulate the cod-like population used in the case study presented here.

@@

Abundance is simulated using the `sim_abundance` function and the settings used for our case study are shown in Table \@ref(tab:par). These settings are also the defaults of the function. This function has a simple structure and requires the specification of a series of `ages` and `years` along with functions for simulating recruitment (`R`), total mortality (`Z`) and growth (`growth`). The package includes the functions `sim_R`, `sim_Z` and `sim_vonB` for simulating recruitment, total mortality and growth, respectively. These functions are "closures" [i.e. functions that contain data and return functions; @wickham2014] and this structure was chosen to avoid the repeated specifications of ages and years. The use of closures also allows users to use their own closures with a similar structure but different underlying formula. Overall, the function provides a simple tool for simulating a range dynamic age-structured populations. For instance, below we simulate a relatively long and short lived species:

```{r, echo = TRUE, eval = TRUE}
set.seed(438)
a <- sim_abundance(ages = 1:20,
                   R = sim_R(mean = 3e+07),
                   Z = sim_Z(mean = 0.5))
b <- sim_abundance(ages = 1:6,
                   R = sim_R(mean = 1e+10),
                   Z = sim_Z(mean = 0.8))
```

@@

The package also includes several plotting function for making quick plotly-based [@sievert2018] interactive visuals of the simulated population. The plots output from the below code are combined into Figure \@ref(fig:surface).

@@

```{r surface, fig.cap = "- Plots produced by `plot_surface` when supplied an list produced by `sim_abundance` with settings that simulate a relatively a) long and b) short lived species. The abundance at age matrix (`N`) is displayed by default; the `mat` argument can be used to specify another matrix contained within the supplied list, such as `Z`."}

set.seed(438)
a <- sim_abundance(ages = 1:20,
                   R = sim_R(mean = 3e+07),
                   Z = sim_Z(mean = 0.5))
b <- sim_abundance(ages = 1:6,
                   R = sim_R(mean = 1e+10),
                   Z = sim_Z(mean = 0.8))

@@

export_plot(p, file = "analysis/paper/figures/plot_surface.png", width = 800, height = 370)
knitr::include_graphics("figures/plot_surface.png")

@@

The `make_grid` function is used to generate a survey grid for use in the `sim_distribution` function. The output from `make_grid` is a raster object [@hijmans2016] with four layers: `depth`, `cell`, `division` and `strat`. If a more detailed and realistic grid is required, users can manually generate their own survey grid using real data and this grid can be supplied to `sim_distribution` if the same structure is used. The settings used to make the grid used in our case study are shown in Table \@ref(tab:par) and these settings are also the defaults. Below we generate and plot (combined in Figure \@ref(fig:grid)) a default grid and another grid with four divisions and a more linear gradient in depth.

@@

```{r grid, fig.cap = "- Plots produced by `plot_grid` when supplied an raster object produced by `make_grid` a) using default settings and b) settings that generate a more linear depth gradient. In these plots, the color gradient represents depth, the grey lines deliniate divisions and white lines deliniate strata."}

@@

export_plot(p, file = "analysis/paper/figures/plot_grid.png", width = 800, height = 430)
knitr::include_graphics("figures/plot_grid.png")

@@

```{r, echo = TRUE, eval = TRUE, cache = TRUE}

@@

```{r distribution, fig.cap = "- Distribution plots of a population simulated using `sim_distribution` that forms a) tight clusters with stronger correlation through years than ages, and b) relatively diffuse clusters with stronger correlation through ages than years."}

@@

export_plot(p, file = "analysis/paper/figures/plot_distribution.png", width = 600, height = 300)
knitr::include_graphics("figures/plot_distribution.png")

@@

The function `sim_survey` can be used to simulate data from one survey over a population simulated using `sim_distribution`. This function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Multiple simulations of the same survey can be run using the `n_sims` argument, however, it is important not to request large numbers of simulations because this function can quickly deplete a computers RAM. Defaults used in the function and for the case study roughly correspond to the assumed catchability in NAFO division 3Ps as well as the sampling protocol used in the survey of this stock (Table \@ref(tab:par)). Below we use `sim_survey` to simulate two surveys over the same population, of which one is set-up to have higher sampling effort than the other.

```{r, echo = TRUE, eval = TRUE, cache = TRUE}

@@

```{r survey, fig.cap = "- Bubble plots and histograms of set catches produced by `plot_survey` when supplied survey data simulated using `sim_survey` under relatively a) high and b) low sampling effort. Histograms of length and age composition include the distribution caught and sampled overlaid with a line of the true distribution of length and ages available to the survey. Note that the first simulation of the survey in year 20 is depicted here."}

@@

@@

Assuming a stratified analysis as the default method for obtaining an index of abundance, a series of survey protocol can be tested using the `test_surveys` function. Provided a simulated population from `sim_distribution` and a series of survey protocol from `expand_surveys`, this function will simulate and analyze data from each survey using the `sim_survey`, `run_strat` and `strat_error` functions. Like `sim_survey_parallel`, this function operates in parallel and allows the specification of `n_sims` and `n_loops`, and the product of these two arguments equals the number of times each survey is simulated. Keep in mind that low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower, especially if the work is spread across few `cores`. The below code will run a small subset of the simulation tests run for the case study presented in this paper (see Table \@ref(tab:par) for code to replicate the case study results). Specifically, `expand_surveys` sets up a series of eight surveys to test (i.e. all possible combinations of `set_den`, `lengths_cap` and `ages_cap` protocol) and the `test_surveys` function will run 250 simulations of each survey and compare stratified estimates of abundance to the true abundance available to the survey. Though a limited test, this may take a while to run.

@@

surveys <- expand_surveys(set_den = c(1, 2) / 1000,
                          lengths_cap = c(100, 500),
                          ages_cap = c(5, 20))

tests <- test_surveys(pop, surveys = surveys,
                      n_sims = 5, n_loops = 50, cores = 2)

@@

Processing time will system (i.e. amount of RAM and number of cores) and setting (i.e. `n_loops` and `n_sims` ratio) dependent. The `test_survey` function will print a progress bar, generated using the progress package [@csardi2016], which details percent completion and will also include an eta after the first step of the loop completes. Thousands of simulations of hundreds of survey designs, like run here for our case study, may take days to run. The `test_surveys` function therefore includes an option for exporting intermediate results to a local directory, via the `export_dir` argument, and the `resume_test` function can be used resume a `test_surveys` run that had to be stopped part way through the process. The final object produced will be a list that includes all objects from `sim_abundance` and `sim_distribution` with the table of survey designs tested (named `surveys`) and tables produced by `strat_error` that end with the names `_strat_error` and `_strat_error_stats`. These tables include a `survey` column to allow merging of the survey protocol table with the error tables. Objects produced by `sim_survey` (set and sampling details) and `run_strat` (full stratified analysis results) are not retained to minimize object size. Like other core functions, some convenience functions are included in SimSurvey for creating interactive plots of the results from `test_surveys`. These will be demonstrated in the [Results] section using the results from the case study.

@@

```{r data, cache = TRUE}
load("analysis/cod_sim_exports/2018-10-26_age_clust_test/test_output.RData")
tests <- sim
```

A dynamic population that varies across ages, time and space was simulated with the parameter settings used here (Table \@ref(tab:par)). Figure \@ref(fig:sp) depicts the aggregate distribution of the population in one year of the simulation and the corresponding catches of one stratified random survey over this population. Layered within this, of course, is the distributions of each age, as well as age and length sampling details. Though age-specific details are not depicted for simplicity, the general pattern of spatial aggregation apparent in Figure \@ref(fig:sp) is similar across all ages. That is, all ages tend to aggregate in fairly dense clusters and low-density zones are fairly wide ranging. The survey, therefore, tends to be characterized by regions with large catches interspersed with regions of no catch (Figure \@ref(fig:sp)). The samples within each successful set are also dynamic and rarely include all age groups. This is because only moderate correlation was imposed on the distributions of ages 1-5+, allowing individuals of different ages to occupy different locations. This results in an intra-haul correlation of approximately `r sim_icc`, which, in this case, is of equal magnitude to the intra-haul correlation observed across more than 20 years of survey data of 3Ps cod.

The stratified analyses run on these simulated data provided estimates of total abundance, abundance at length and abundance at age, and different stages of sampling affect these estimates. Specifically, set density affects all estimates, length sampling affects estimates of abundance at length and abundance at age, and age sampling affects abundance at age estimates. Figure \@ref(fig:tot) depicts the consequences of different set densities on the estimates of total abundance available to the survey through the simulated series. It is clear from this figure that the probability envelopes are tighter (i.e. estimates are more precise) and bias is negligible. Likewise, abundance at length and abundance at age estimates are more precise as set density is increased (Figure \@ref(fig:length), \@ref(fig:age), \@ref(fig:year)). With the exception of a length sampling protocol of 10 measurements per set ($M_{lengths}$ = 10), there appears to be little difference in the estimates of abundance at length when the number of measurements are capped at 100 ($M_{lengths}$ = 100) or 1000 ($M_{lengths}$ = 1000; Figure \@ref(fig:length)). Some downward bias is apparent in the abundance at length estimates, especially at larger lengths, under the low to medium set density scenarios with low length sampling effort ($D_{sets}$ = 0.0005 or 0.002 and $M_{lengths}$ = 10; Figure \@ref(fig:length)). Upward or downward bias in abundance at age estimates is apparent in all cases except the high set density and high length sampling scenario ($D_{sets}$ = 0.01 and $M_{lengths}$ = 1000; Figure \@ref(fig:age), \@ref(fig:year)). Under both low and medium set densities ($D_{sets}$ = 0.0005 and 0.02, respectively), increasing length sampling effort from 10 or 100 measurements per set to 1000 appears to increase bias or reduce precision slightly (Figure \@ref(fig:age), \@ref(fig:year)).

>>>>

```{r setup, include=FALSE}

# devtools::install_github("rstudio/rmarkdown@v1.10")
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      dev = "png",
                      dpi = 300)
knitr::opts_knit$set(root.dir = "../..")
options(scipen = 999) # turn off scientific notation to simplify printing

```{r packages, include = FALSE}

library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
Sys.setenv("MAPBOX_TOKEN" = "pk.eyJ1IjoicGF1bHJlZ3VsYXIiLCJhIjoiY2pueGIxejMxMGM0MjNqbjR1aXdwYm92bSJ9.R-t1SCa0VHKf4N-PQmYI5Q")
source("analysis/paper/helper_functions.R")

replot <- FALSE # plot the figures again? (acts as a manual cache)

@@

The construction of the SimSurvey package was motivated by a regional need for assessing the sampling design of trawl surveys conducted along the Newfoundland and Labrador shelf by Fisheries and Oceans Canada. As a tangible first step, we focused our efforts on emulating data from the survey of cod in NAFO division 3Ps since it is one of the most dynamic and heavily sampled stocks in the region. Below we outline the equations behind a series of SimSurvey functions that were used to simulate survey data with similar features to data obtained by the survey of 3Ps cod. The settings were iteratively modified until it was difficult to distinguish the simulated data from real survey data; these values were set as the defaults for the main functions in the package. Here we evaluate the efficacy of alternate sampling protocol by assessing deviation between stratified estimates of abundance [@Smith1981] from the true abundance available to the survey. While assessing model-based analyses was an option, we focused on the design-based stratified analysis for simplicity and because of its widespread use. See Table \@ref(tab:par) for a description of the code used to generate the case study results.

Table: (\#tab:par) - Main function calls, with argument descriptions and associated parameter symbols, used to simulate the cod-like population used in the case study presented here. Note that the settings below largely correspond with the defaults used in the functions.

@@

Abundance is simulated using the `sim_abundance` function and the settings used for our case study are shown in Table \@ref(tab:par). These settings are also the defaults of the function. This function has a simple structure and requires the specification of a series of `ages` and `years` along with functions for simulating recruitment (`R`), total mortality (`Z`) and growth (`growth`). The package includes the functions `sim_R`, `sim_Z` and `sim_vonB` for simulating recruitment, total mortality and growth, respectively. These functions are "closures" [i.e. functions that contain data and return functions; @wickham2014] and this structure was chosen to avoid the repeated specifications of ages and years. The use of closures also allows users to use their own closures with a similar structure but different underlying formula. Overall, the function provides a simple tool for simulating a range dynamic age-structured populations. For instance, below we simulate a relatively long (default case study settings) and short lived species.

```{r, echo = TRUE, eval = replot}
set.seed(438)
a <- sim_abundance(ages = 1:20,
                   R = sim_R(mean = 3e+07),
                   Z = sim_Z(mean = 0.5))
b <- sim_abundance(ages = 1:6,
                   R = sim_R(mean = 1e+10),
                   Z = sim_Z(mean = 0.8))
```

@@

The package also includes several plotting function for making quick plotly-based [@sievert2018] interactive visuals of the simulated population. For instance, the `plot_surface` function can be used to make quick visuals of matricies contained within the list returned by `sim_abundance`. The plots output from the below code are combined into Figure \@ref(fig:surface). Here we display the abundance at age matrix (object named `N` in the list produceb by `sim_abundance`); other names can be supplied to the `mat` argument to visualize a different matrix from the `sim_abundance` list, such as `Z`.

@@

```{r, eval = replot}
set.seed(438)
a <- sim_abundance(ages = 1:20,
                   R = sim_R(mean = 3e+07),
                   Z = sim_Z(mean = 0.5))
b <- sim_abundance(ages = 1:6,
                   R = sim_R(mean = 1e+10),
                   Z = sim_Z(mean = 0.8))

@@

export_plot(p, file = "analysis/paper/figures/plot_surface.png", width = 800, height = 370)
```

```{r surface, fig.cap = "- Surface plots of simulated abundance at age of a relatively a) long lived (case study settings) and b) short lived species. These plots were produced by `plot_surface` when supplied a list produced by `sim_abundance`."}

knitr::include_graphics("figures/plot_surface.png")

@@

The `make_grid` function is used to generate a survey grid for use in the `sim_distribution` function. The output from `make_grid` is a raster object [@hijmans2016] with four layers: `depth`, `cell`, `division` and `strat`. If a more detailed and realistic grid is required, users can manually generate their own survey grid using real data and this grid can be supplied to `sim_distribution` if the same structure is used. The package includes a manually constructed survey grid of NAFO division 3Ps (named `survey_grid`) and the data-raw folder in the GitHub directory includes the data and code used to construct this grid. However, for simplicity, we use `make_grid` to construct a square grid for our case study and the settings used are shown in Table \@ref(tab:par). Below we generate and plot (combined in Figure \@ref(fig:grid)) a default case study grid and another grid with four divisions and a more linear gradient in depth.

@@

```{r eval = replot}

@@

export_plot(p, file = "analysis/paper/figures/plot_grid.png", width = 800, height = 430)

```{r grid, fig.cap = "- Plots produced by `plot_grid` when supplied an raster object produced by `make_grid` a) using default case study settings and b) settings generates a grid with four divisions and a more linear depth gradient. In these plots, the color gradient represents depth, the grey lines deliniate divisions and white lines deliniate strata."}

knitr::include_graphics("figures/plot_grid.png")

@@

```{r, echo = TRUE, eval = replot}

@@

```{r, eval = replot}

@@

export_plot(p, file = "analysis/paper/figures/plot_distribution.png", width = 600, height = 300)

```{r distribution, fig.cap = "- Distribution plots of simulated populations that form a) tight clusters with stronger correlation through years than ages (case study settings), and b) relatively diffuse clusters with stronger correlation through ages than years. This plot is a facet of plots produced by `plot_distribution` when supplied simulations from `sim_distribution`."}

knitr::include_graphics("figures/plot_distribution.png")

@@

The function `sim_survey` can be used to simulate data from one survey over a population simulated using `sim_distribution`. This function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Multiple simulations of the same survey can be run using the `n_sims` argument, however, it is important not to request large numbers of simulations because this function can quickly deplete a computers RAM. Defaults used in the function and for the case study roughly correspond to the assumed catchability in NAFO division 3Ps as well as the sampling protocol used in the survey of this stock (Table \@ref(tab:par)). Below we use `sim_survey` to simulate two surveys over our case study population, of which one is set-up to have higher sampling effort than the other.

```{r, echo = TRUE, eval = replot}

@@

```{r eval = replot}

@@

```{r survey, fig.cap = "- Bubble plots and histograms of set catches from a simulated stratified-random survey of the case study population under relatively a) high and b) low sampling effort. Histograms of length and age composition include the distribution caught and sampled overlaid with a line of the true distribution of length and ages available to the survey. Note that the first simulation of the survey in year 20 is depicted here. These plots are produced by `plot_survey` when supplied survey data simulated using `sim_survey`."}

@@

Assuming a stratified analysis as the default method for obtaining an index of abundance, a series of survey protocol can be tested using the `test_surveys` function. Provided a simulated population from `sim_distribution` and a series of survey protocol from `expand_surveys`, this function will simulate and analyze data from each survey using the `sim_survey`, `run_strat` and `strat_error` functions. Like `sim_survey_parallel`, this function operates in parallel and allows the specification of `n_sims` and `n_loops`, and the product of these two arguments equals the number of times each survey is simulated. Keep in mind that low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower, especially if the work is spread across few `cores`. Because most of the default settings of the functions match the case study settings, the below code will replicate the results from our case study (see Table \@ref(tab:par) for a more detail). The `expand_surveys` function sets up a series of `r nrow(expand_surveys())` surveys to test (i.e. all possible combinations of `set_den`, `lengths_cap` and `ages_cap` protocol) and the `test_surveys` function will run 1000 simulations of each survey and compare stratified estimates of abundance to the true abundance available to the survey.

@@

surveys <- expand_surveys(set_den = c(0.0005, 0.001, 0.002, 0.005, 0.01),
                          lengths_cap = c(5, 10, 20, 50, 100, 500, 1000),
                          ages_cap = c(2, 5, 10, 20, 50))

tests <- test_surveys(pop, surveys = surveys,
                      n_sims = 5, n_loops = 200, cores = 2)

@@

```{r data, eval = replot}

load("analysis/cod_sim_exports/2018-10-26_age_clust_test/test_output.RData")
tests <- sim

Processing time will system (i.e. amount of RAM and number of cores) and setting (i.e. `n_loops` and `n_sims` ratio) dependent. The `test_survey` function will print a progress bar, generated using the progress package [@csardi2016], which details percent completion and will also include an eta after the first step of the loop completes. Keep in mind that thousands of simulations of hundreds of survey designs may take days to run. The `test_surveys` function therefore includes an option for exporting intermediate results to a local directory, via the `export_dir` argument, and the `resume_test` function can be used resume a `test_surveys` run that had to be stopped part way through the process. The final object produced will be a list that includes all objects from `sim_abundance` and `sim_distribution` with the table of survey designs tested (named `surveys`) and tables produced by `strat_error` that end with the names `_strat_error` and `_strat_error_stats`. These tables include a `survey` column to allow merging of the survey protocol table with the error tables. Objects produced by `sim_survey` (set and sampling details) and `run_strat` (full stratified analysis results) are not retained to minimize object size. Like other core functions, some convenience functions are included in SimSurvey for creating interactive plots of the results from `test_surveys`. For instance a series of plotting functions ending in `_fan` produces fancharts where stratified estimates of abundance from each simulated survey are converted into a series of quantiles to depict the probability that estimates fall within a praticular range. True values of abundance available to the survey are overlaid on the series of probability envelopes. These plots help visually assess the level of percision and bias from a specific set of survey protocol. The three lines of code below will produce interactive fancharts for stratified estimates of total abundance, abundance at length and abundance at age, respectively. A subset of these plots have been combined into static plots (Figure \@ref(fig:fan1), \@ref(fig:fan2), \@ref(fig:fan3)).

plot_total_strat_fan(tests)
plot_length_strat_fan(tests, years = 1:20, lengths = 1:100)
plot_age_strat_fan(tests, years = 1:20, ages = 1:10)

```{r eval = replot}

surveys <- tests$surveys
set_dens <- c(0.0005, 0.002, 0.01)
i <- surveys$survey[surveys$set_den == set_dens[1] & surveys$lengths_cap == 10 & surveys$ages_cap == 10] # lengths_cap and ages_cap does not matter here
a <- plot_total_strat_fan(tests, surveys = i)
i <- surveys$survey[surveys$set_den == set_dens[2] & surveys$lengths_cap == 10 & surveys$ages_cap == 10]
b <- plot_total_strat_fan(tests, surveys = i)
i <- surveys$survey[surveys$set_den == set_dens[3] & surveys$lengths_cap == 10 & surveys$ages_cap == 10]
c <- plot_total_strat_fan(tests, surveys = i)

p <- subplot(a, b, c, nrows = 1, shareY = TRUE, titleX = FALSE) %>% 
  add_labels(x = 0.5, y = 0, text = "Year", yshift = -40) %>% 
  add_labels(x = c(0.1, 0.5, 0.9), y = rep(1, 3), yshift = 20, 
             text = paste("D<sub>sets</sub> =", set_dens))

export_plot(p, file = "analysis/paper/figures/plot_total_strat_fan.png", width = 700, height = 250)

```{r fan1, fig.cap = "- Fanchart of stratified estimates of the trend in total abundance from surveys with different set densities, $D_{sets}$. The heavy dark line indicates the true tred in the total population available to the survey and the color gradient represents a range of probability envelopes from 10% to 90%. This plot is a facet of plots produced by `plot_total_strat_fan` when supplied results from `test_surveys`."}

knitr::include_graphics("figures/plot_total_strat_fan.png")

```{r eval = replot}

facet_fan <- function(data, ages = NULL, lengths = NULL, ylim = NULL, set_dens = c(0.0005, 0.002, 0.01), lengths_caps = c(10, 100, 1000)) {
  surveys <- data$surveys
  s <- expand.grid(set_den = set_dens, lengths_cap = lengths_caps)
  plot_list <- vector("list", nrow(s))
  for (i in seq_along(set_dens)) {
    for (j in seq_along(lengths_caps)) {
      s_i <- surveys$survey[surveys$set_den == set_dens[i] & surveys$lengths_cap == lengths_caps[j] & surveys$ages_cap == 10]
      if (is.null(ages)) {
        p <- plot_length_strat_fan(data, surveys = s_i, years = 7, lengths = lengths) %>% 
         layout(yaxis = list(range = ylim))
      } else {
        p <- plot_age_strat_fan(data, surveys = s_i, years = 7, ages = ages) %>% 
          layout(yaxis = list(range = ylim))
      }
      plot_list[[which(s$set_den == set_dens[i] & s$lengths_cap == lengths_caps[j])]] <- p
    }
  }
  subplot(plot_list, nrows = length(set_dens), shareX = TRUE, shareY = TRUE, titleX = FALSE, titleY = FALSE)
}

p <- facet_fan(tests, lengths = 1:100, ylim = c(0, 21000000)) %>% 
  layout(margin = list(r = 30)) %>% 
  add_labels(x = c(0.1, 0.5, 0.9), y = rep(1, 3), yshift = 20, 
             text = paste("D<sub>sets</sub> =", c(0.0005, 0.002, 0.01))) %>% 
  add_labels(x = rep(1, 3), y = c(0.05, 0.5, 0.95), xshift = 30, textangle = 90,
             text = paste("M<sub>lengths</sub> =", rev(c(10, 100, 1000)))) %>% 
  add_labels(x = 0.5, y = 0, text = "Year", yshift = -40) %>% 
  add_labels(x = 0, y = 0.5, text = "Abundance index", xshift = -60, textangle = -90)

export_plot(p, file = "analysis/paper/figures/plot_length_strat_fan.png", width = 700, height = 600)

```{r fan2, fig.cap = "- Fanchart of stratified estimates of abundance at length from year seven of the simulation from surveys with different set densities, $D_{sets}$, and length sampling protocol, $M_{lengths}$. The heavy dark line indicates the true tred in the total population available to the survey and the color gradient represents a range of probability envelopes from 10% to 90%. This plot is a facet of plots produced by `plot_total_strat_fan` when supplied results from `test_surveys`."}

knitr::include_graphics("figures/plot_length_strat_fan.png")

```{r, eval = replot}

p <- facet_fan(tests, ages = 1:10, ylim = c(0, 51000000)) %>% 
  layout(margin = list(r = 30)) %>% 
  add_labels(x = c(0.1, 0.5, 0.9), y = rep(1, 3), yshift = 20, 
             text = paste("D<sub>sets</sub> =", c(0.0005, 0.002, 0.01))) %>% 
  add_labels(x = rep(1, 3), y = c(0.05, 0.5, 0.95), xshift = 30, textangle = 90,
             text = paste("M<sub>lengths</sub> =", rev(c(10, 100, 1000)))) %>% 
  add_labels(x = 0.5, y = 0, text = "Year", yshift = -40) %>% 
  add_labels(x = 0, y = 0.5, text = "Abundance index", xshift = -60, textangle = -90)

export_plot(p, file = "analysis/paper/figures/plot_age_strat_fan.png", width = 700, height = 600)

```{r fan3, fig.cap = "- Fanchart of stratified estimates of the trend in abundance at age four from surveys with different set densities, $D_{sets}$, and length sampling protocol, $M_{lengths}$. Number of ages sampled per length group, $M_{ages}$, was 10 in all scenarios. The heavy dark line indicates the true tred in the total population available to the survey and the color gradient represents a range of probability envelopes from 10% to 90%. This plot is a facet of plots produced by `plot_total_strat_fan` when supplied results from `test_surveys`."}

knitr::include_graphics("figures/plot_age_strat_fan.png")

@@

- Make the results more general, almost about the flexibility of the package, then hone in on the case study??

A dynamic population that varies across ages, time and space was simulated with the parameter settings used here (Table \@ref(tab:par)). Because the default settings of the functions match the case study settings, Figure \@ref(fig:surface)a depicts abundance at age through time and Figure \@ref(fig:distribution)a depicts the spatial distribution of ages 1-3 through years 1-3. In general, the parameter settings used dictate that all ages tend to aggregate in fairly dense clusters and that low-density zones are relatively wide-ranging. Surveys, therefore, tend to be characterized by regions with large catches interspersed with regions of no catch (Figure \@ref(fig:survey)). The samples within each successful set are also dynamic and rarely include all age groups. This is because only moderate correlation ($\varphi_{\xi, age}$ of 0.5) was imposed on the distributions of ages 1-5+, allowing individuals of different ages to occupy different locations. These settings were chosen to simulated data that roughly correspond to actual survey data of cod from NAFO division 3Ps, where cod between the ages of 1-5 tend to be caught at different locations.

The stratified analyses run on these simulated data provided estimates of total abundance, abundance at length and abundance at age, and different stages of sampling affect these estimates. Specifically, set density affects all estimates, length sampling affects estimates of abundance at length and abundance at age, and age sampling affects abundance at age estimates. This is because stratified estimates of total abundance is based on aggregate catch while abundance at length estimates requires the length frequency data and abundance at age estimates requires both length and age data to construct an age-length key.

Figure \@ref(fig:tot) depicts the consequences of different set densities on the estimates of total abundance available to the survey through the simulated series. It is clear from this figure that the probability envelopes are tighter (i.e. estimates are more precise) and bias is negligible. Likewise, abundance at length and abundance at age estimates are more precise as set density is increased (Figure \@ref(fig:length), \@ref(fig:age), \@ref(fig:year)). With the exception of a length sampling protocol of 10 measurements per set ($M_{lengths}$ = 10), there appears to be little difference in the estimates of abundance at length when the number of measurements are capped at 100 ($M_{lengths}$ = 100) or 1000 ($M_{lengths}$ = 1000; Figure \@ref(fig:length)). Some downward bias is apparent in the abundance at length estimates, especially at larger lengths, under the low to medium set density scenarios with low length sampling effort ($D_{sets}$ = 0.0005 or 0.002 and $M_{lengths}$ = 10; Figure \@ref(fig:length)). Upward or downward bias in abundance at age estimates is apparent in all cases except the high set density and high length sampling scenario ($D_{sets}$ = 0.01 and $M_{lengths}$ = 1000; Figure \@ref(fig:age), \@ref(fig:year)). Under both low and medium set densities ($D_{sets}$ = 0.0005 and 0.02, respectively), increasing length sampling effort from 10 or 100 measurements per set to 1000 appears to increase bias or reduce precision slightly (Figure \@ref(fig:age), \@ref(fig:year)).
